The ANthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-12-22 paper.tex
add TA links

\begin{table}[b]
\centering
\caption{Statistical information. Column values do not add up because some entities are defined in both subontologies.}
\label{tab:stats}
\begin{tabulary}{\textwidth}{lSSSSSS}
\toprule
Ontology	&\textnormal{Classes}	&\textnormal{Object properties}	&\textnormal{Data properties}	&\textnormal{Individuals}	&\textnormal{Annotation properties}	&\textnormal{Axioms}\\
\midrule
ANNOdc		&41						&18								&1								&0							&19									&178\\
ANNOds		&1166					&11								&0								&803						&43									&18231\\
\midrule
combined	&1195					&21								&1								&803						&53									&18382\\
\bottomrule
\end{tabulary}
\end{table}

>>>>

\begin{table}[b]
\centering
\caption{Statistical information. Column values do not add up because some entities are defined in both subontologies.}
\label{tab:stats}
\begin{tabulary}{\textwidth}{lSSSSSSSS}
\toprule
Ontology	&\textnormal{Classes}	&\textnormal{Object properties}	&\textnormal{Data prop.}	&\textnormal{Individuals}	&\textnormal{Annotation prop.}	&\textnormal{Axioms}	&\textnormal{FMA links}				&\textnormal{TA links}\\
\midrule
ANNOdc		&41						&18								&1								&0							&19									&178					&11							&0\\
ANNOds		&1166					&11								&0								&803						&43									&18231					&503						&206\\
\midrule
combined	&1195					&21								&1								&803						&53									&18382					&514						&206\\
\bottomrule
\end{tabulary}
\end{table}
